Predicting Conflict Escalation

### 2023-05-02 docs/hes_final/article.qmd
Extend metrics figure title for interpretation

![Model performance metrics](imgs/tbl-best-max-metrics.png){width=50%}

![Model performance metrics](imgs/tbl-best-min-metrics.png){width=50%}

>>>>

![Model performance metrics (higher values are better)](imgs/tbl-best-max-metrics.png){width=50%}

![Model performance metrics (lower values are better)](imgs/tbl-best-min-metrics.png){width=50%}
